---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CovidRaceData

<!-- badges: start -->
![R-CMD-check](https://github.com/Oliver-BE/CovidRaceData/workflows/R-CMD-check/badge.svg)
<!-- badges: end -->

The `CovidRaceData` package contains two data sets on the COVID-19 pandemic in the US by race/ethnicity. More specifically, it has data for the number of COVID-19 cases and deaths by race/ethnicity for each state. 

The raw data set (`covid_race_data_raw`) was obtained from [The COVID Tracking Project](https://covidtracking.com/race/about#download-the-data) and contains the number of COVID-19 cases and deaths by race/ethnicity by US state (as well as each state's population).

The `aggregated_covid_race_df` contains information on the percent of cases/deaths by race/ethnicity vs. the percent of the population that each race/ethnicity composes in the US.

## Installation

You can install the released version of CovidRaceData from [CRAN](https://CRAN.R-project.org) with:

``` r
# install.packages("remotes")
remotes::install_github("Oliver-BE/CovidRaceData")
```

## Example usage

This is a basic example which shows you how to solve a common problem:

```{r example}
library(CovidRaceData)
## basic example code
```

